\vspace{1.0cm} \LARGE \bf MERS-CoV spillover at the camel-human interface

### 2017-11-29 mers-structure.tex
Reorder some supplementary figures.

We performed a smaller set of simulations with 2500 replicates and twice the number of cases, \textit{i.e.} $\sum_{i=1}^{K} C_{i} = 4000$, to explore a dramatically underreported epidemic.
Additionally, we performed additional smaller set of simulations on a rougher grid of $R_{0}$ values (23 values, 0.50--1.05), with 5 values of dispersion parameter $\omega$ (0.002, 0.04, 0.1, 0.5, 1.0) and 3 levels of bias (1, 2, 3) to justify our choice of dispersion parameter $\omega$ that was fixed to 0.1 in the main analyses.

@@

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.65\textwidth]{figures/mers_prior.png}
	\caption{\textbf{Posterior migration rate estimates for two choices of prior.}
Negligible flow of MERS-CoV lineages from humans into camels is recovered regardless of prior choice.
Plots show the 95\% highest posterior density for the estimated migration rate from the human deme into the camel deme (blue) and \textit{vice versa} (orange).
Dotted lines indicate exponential priors specified for migration rates, with mean 1.0 (bottom) or 10.0 (top).
	}
	\label{prior}
\end{figure}

>>>>

We performed a smaller set of simulations with 2500 replicates and twice the number of cases, \textit{i.e.} $\sum_{i=1}^{K} C_{i} = 4000$, to explore a dramatically underreported epidemic.
Additionally, we performed additional smaller set of simulations on a rougher grid of $R_{0}$ values (23 values, 0.50--1.05), with 5 values of dispersion parameter $\omega$ (0.002, 0.04, 0.1, 0.5, 1.0) and 3 levels of bias (1, 2, 3) to justify our choice of dispersion parameter $\omega$ that was fixed to 0.1 in the main analyses (Figure \ref{marginals}).

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.65\textwidth]{figures/mers_prior.png}
	\caption{\textbf{Posterior backwards migration rate estimates for two choices of prior.}
Negligible flow of MERS-CoV lineages from humans into camels is recovered regardless of prior choice (note that rates are backwards in time).
Plots show the 95\% highest posterior density for the estimated migration rate from the human deme into the camel deme looking backwards in time (orange) and \textit{vice versa} (blue).
Dotted lines indicate exponential priors specified for migration rates, with mean 1.0 (bottom) or 10.0 (top).
	}
	\label{prior}
\end{figure}

@@
